Supermartingales and Termination Analysis of Statistical PCF

### 2020-09-17 probabilisticProgrammingMartingales.tex
minor

        \item $N \mid P = \tY (\lambda x. A)$, $A$ reduced at $Q$ is $A'$, $(R_i)_i$ is a list of all the positions where $A' \mid R  = x$, ordered from left to right, $O_1$ is $N$ reduced first at $P;\tY;\lambda;Q$ then at $P$, and $O_2$ is $N$ reduced first at $P$ then at $P;\lambda;@_1;Q$ then at $P;\lambda;@_1;R_i;Y;\lambda;Q$ for each $i$ in order.
    \end{enumerate}
    (in which case $O_1$ and $O_2$ are equal as terms, but with different reduction sequences), $O_1'$ and $O_2'$ are the results of applying some reduction sequence to each of $O_1$ and $O_2$ (the same reductions in each case, which is always possible because they're equal terms), and $S$ is a position in $O_1'$ (or equivalently $O_2'$), then $(O_1',S) \sim_c (O_2',S)$.
\end{enumerate}
The $\sim_c$-rules are illustrated in the following diagrams.
\end{definition}

\include{sim-diagram}

@@

Unlike in the purely call-by-value case, the version of the reduction relation that takes into account samples is still a general relation rather than a function, so it is denoted ``$\Rightarrow$'' instead of ``$\red$'', and it relates $\biguplus_{M \in \Lambda_0} I^{L_s(M)}$ to itself.
\changed[lo]{We write an element of $\biguplus_{M \in \Lambda_0} I^{L_s(M)}$ as $(M', s)$ where the term $M' \in \Lambda^0$ identifies the component of the disjoint set, and $s \in  I^{L_s(M')}$.}
\begin{align*}
& (M,s) \Rightarrow (N,s \circ i(M \to N)) \text{ if either} \\
& \qquad \text{$M \to N$ and the redex is not $\tsample$, or} \\
& \qquad \text{$M \mid P = \tsample$, $N = M[\underline{s(Sk(M),P)}/P]$ and $\lambda$ does not occur after $@_2$ or $\tY$ in $P$}
\end{align*}

>>>>

        \item $N \mid P = \tY (\lambda x. A)$, $A$ reduced at $Q$ is $A'$, $(R_i)_i$ is a list of all the positions where $A' \mid R  = x$, ordered from left to right, $O_1$ is $N$ reduced first at $P;\tY;\lambda;Q$ then at $P$, and $O_2$ is $N$ reduced first at $P$ then at $P;\lambda;@_1;Q$ then at $P;\lambda;@_1;R_i;Y;\lambda;Q$ for each $i$ in order.
    \end{enumerate}
    (in which case $O_1$ and $O_2$ are equal as terms, but with different reduction sequences), $O_1'$ and $O_2'$ are the results of applying some reduction sequence to each of $O_1$ and $O_2$ (the same reductions in each case, which is always possible because they're equal terms), and $S$ is a position in $O_1'$ (or equivalently $O_2'$), then $(O_1',S) \sim_c (O_2',S)$.
\end{enumerate}
See \Cref{fig:adk-diagram} for a graphical depiction of $\sim_p$- and $\sim_c$-rules.
\end{definition}

\begin{figure}
\include{sim-diagram}
\caption{\label{fig:adk-diagram} Some examples of the $\sim_p$- and $\sim_c$-rules}
\end{figure}

@@

Unlike in the purely call-by-value case, the version of the reduction relation that takes into account samples is still a general relation rather than a function, so it is denoted ``$\Rightarrow$'' instead of ``$\red$'', and it relates $\biguplus_{M \in \Lambda_0} I^{L_s(M)}$ to itself.
\changed[lo]{We write an element of $\biguplus_{M \in \Lambda_0} I^{L_s(M)}$ as $(M', s)$ where the \emph{term} $M' \in \Lambda^0$ and $s \in  I^{L_s(M')}$.}
\begin{align*}
& (M,s) \Rightarrow (N,s \circ i(M \to N)) \text{ if either} \\
& \qquad \text{$M \to N$ and the redex is not $\tsample$, or} \\
& \qquad \text{$M \mid P = \tsample$, $N = M[\underline{s(Sk(M),P)}/P]$ and $\lambda$ does not occur after $@_2$ or $\tY$ in $P$}
\end{align*}
